---
title: "Showcase: YouTube"
subtitle: "Focus on YouTube Data Tools"
format: 
  html:
    toc: true
    toc-depth: 4
callout-appearance: simple
execute: 
  cache: true
  eval: true
  echo: true
  message: false
  warning: false
highlight-style: atom-one
editor_options: 
  chunk_output_type: console
---

## Background

Practical application of the YouTube Data Tool (YTDT) using the example of Mai Thi Nguyen-Kim ( [{{< fa brands twitter >}}](https://twitter.com/maithi_nk) \| [{{< fa brands instagram >}}](https://www.instagram.com/maithink/) ) and her [{{< fa brands youtube >}}](https://www.youtube.com/c/maiLab)-Channel [maiLab](https://www.youtube.com/c/maiLab).

#### Assignments

1.  Use the Channel Search Function of the YTDT to find the correct `channel ID` for [{{< fa brands youtube >}}](https://www.youtube.com/c/maiLab)-Channel [maiLab](https://www.youtube.com/c/maiLab). Therefore, enter "*mailab*" in the field `search query` and download the results as `.csv`. Open the file and search extract the correct channel ID.\
    If in doubt, use `Channel Info` function to check if the selected ID matches the channel description.

## Preparation

### Load necessary packages

```{r load packages}
library(tidyverse) # Preparation of the data
library(quanteda) # Text mining
library(quanteda.textstats) # Text statistics
library(quanteda.textplots) # Visualisation of text data
library(readr) # Data import
library(here)
library(sjmisc)
library(lubridate)
library(ggthemes)
library(ggpubr)
```

## Identify `Channel ID`

### Import data

From `Channel Search` results from YTDT

```{r}
channel_search <- read_csv(
  here(
    "content/05-api_access-youtube/data/channelsearch_channels50_2022_11_16-19_45_44.csv"))

# Preview
channel_search %>% glimpse
```

### Explorative analysis

#### Identify correct ID

```{r}
# Overview
channel_search %>%
  select(position , id, title)
```

## Get channel video list

### Import data

```{r}
video_list <- read_csv(
  here(
    "content/05-api_access-youtube/data/videolist_channel186_2022_11_16-20_50_14.csv"))

# Preview
video_list %>% glimpse
```

### Explorative analysis

#### Video uploads over time

```{r}

```
